On optimisation in HDR brachytherapy

### 2015-03-05 Paper BMT/article-sample-proceedings.tex
Added paragraph on model description.

The aim of this article is to compare three different approaches in HDR-Brachytherapy treatment planning. The three analysed algorithms are linear programming, simulated annealing and genetic algorithms. The results are evaluated by analysing the conformity and homogenity of the dose-distribution as well as runtime for different parameters.

>>>>

The aim of this article is to compare three different approaches in HDR-Brachytherapy treatment planning. The three analysed algorithms are linear programming, simulated annealing and genetic algorithms. The results are evaluated by analysing the conformity and homogeneity of the dose-distribution as well as runtime for different parameters.

\section{Model description}
HDR brachytherapy consists of several radioactive sources being placed inside the patient's body by needles. These sources will eradiate into the surrounding tissues, treating tumor cells and other critical volumes. Therefore, it relies heavily on optimal algorithms to determine the dwell times for certain, predefined goals. \\
The body is represented by an equidistant grid of voxels, defining the single body cell type. The seeds are randomly positioned within the tumor voxels. Hence, the dosis in a voxel is calculated as a sum of each seed by evaluating the dose-function up to a fixed limit, where the influence gets negligible.
